Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-08 paper/ms.tex
Fix formatting issues

What about \sunanalog?
\sunanalog\ is also enhanced in \elem{Li} considering its age of
$4.00_{-1.56}^{+1.51}$~Gyr than the nominal \elem{Li} depletion predics by
$\approx 1$~dex.
This enhancement puts an upper limit on the accreted mass to be
$\approx 4$~\mearth assuming \elem{Li} concentration of $1.1$~ppm
(\citealt{mcdonough2001composition}).
Unlike \bizarreone, we cannot know the pre-accretion abundances of \sunanalog
\footnote{
  Strictly speaking, we can never know the pre-accretion abundances
  for \bizarreone\ either.
  We only have an {\it approximate} idea that this is not far from a solar-twin
  star \sunanalog, and because the deviation from this ``anchor'' star is
  large, it is reasonable to consider an accretion by the Sun.
  In reality, \sunanalog\ may as well have had its own accretion history,
  which indeed seems to be the case according to its \elem{Li} abundance.
}.
However, we note that the span of abundance difference between highly volatile
elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
as \elem{Fe} expected from accreting $4$~\mearth to the Sun is $\approx
0.05$~dex.
This is comparable to the abundance difference between N, Na and Fe in
\sunanalog.
It is also interesting that \sunanalog\ also shows a deficit in the same
volatile and moderately volatile elements
(\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}) relative to Fe
just as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was much smaller than \bizarreone.

>>>>

What about \sunanalog?
\sunanalog\ is also enhanced in \elem{Li} considering its age of
$4.00_{-1.56}^{+1.51}$~Gyr than the nominal \elem{Li} depletion predics by
$\approx 1$~dex.
This enhancement puts an upper limit on the accreted mass to be
$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
(\citealt{mcdonough2001composition}).
Unlike \bizarreone, we cannot know the pre-accretion abundances of
\sunanalog.\footnote{
  Strictly speaking, we can never know the pre-accretion abundances
  for \bizarreone\ either.
  We only have an {\it approximate} idea that this is not far from a solar-twin
  star \sunanalog, and because the deviation from this ``anchor'' star is
  large, it is reasonable to consider an accretion by the Sun.
  In reality, \sunanalog\ may as well have had its own accretion history,
  which indeed seems to be the case according to its \elem{Li} abundance.
}
However, we note that the span of abundance difference between highly volatile
elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
as \elem{Fe} expected from accreting $4$~\mearth to the Sun is $\approx
0.05$~dex.
This is comparable to the abundance difference between N, Na and Fe in
\sunanalog.
It is also interesting that \sunanalog\ also shows a deficit in the same
volatile and moderately volatile elements
(\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}) relative to Fe
just as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was much smaller than \bizarreone.
